%----------- Experiance ------------

\hTable
{Software Engineer}{Full Time}
{InsuranceDekho}{Jun 2024 --- Present}

\ulStart

\li{Engineered a comprehensive employee benefits dashboard, leveraging \href{https://nextjs.org/docs}{Next.Js}, \href{https://tanstack.com/query/v3}{Tanstack-Query}, \href{https://tanstack.com/table/latest}{Tanstack-Table}, \href{https://react-hook-form.com/}{React-hook-form}, and \href{https://sass-lang.com/}{SCSS} modularization to deliver a scalable and maintainable solution.}

\li{Created reusable UI components using \href{https://www.radix-ui.com/primitives}{``Radix UI Primitives''} and trending libraries like \href{https://daypicker.dev/}{react-day-picker}, \href{https://react-dropzone.js.org/}{dropzone}, etc, leveraging \href{https://cva.style/docs}{``Class Variance Authority'' (CVA)} to create variants for UI components, ensuring a consistent and flexible design system.}

\li{Implemented \href{https://www.sailpoint.com/identity-library/what-is-attribute-based-access-control}{``Attribute-Based Access Control'' (ABAC)} with JWT, securing user access and authorization. Utilized attributes to control component access, ensuring that users interact only with permitted components}

\ulEnd

%----------- Experiance ------------
\hTable
{Code 4 GovTech Contributor}{Open-Source}
{Avanti Fellows}{Jun 2024 --- Sep 2024}

\ulStart
\li{Developed the \href{https://github.com/avantifellows/quiz-creator}{``Session Creator''} platform using \href{https://nextjs.org/docs}{Next.Js} and \href{https://ui.shadcn.com/}{ShadCn UI}, enhancing the efficiency of session management for educators, resulting in a 50\% reduction in manual errors and working.}

\li{Designed and implemented CI/CD pipelines with GitHub Actions, achieving 100\% code consistency through automated linting, formatting, unit testing and end-to-end testing.}

\li{Enabled the creation of over 1000 sessions across multiple regions (Haryana, Punjab, Delhi, etc.) in just 2 months.}
\ulEnd

%----------- Experiance ------------
\hTable
{Software Engineer}{Intern}
{InsuranceDekho}{Oct 2023 --- May 2024}

\ulStart

\li{Architected an buyer-facing web-app utilizing the \href{https://ondc.org/}{ONDC network}, driving insurance sales; incorporated \href{https://nextjs.org/docs}{Next.Js}, \href{https://tanstack.com/query/v3}{Tanstack-Query}, \href{https://react-hook-form.com/}{React-hook-form}, and \href{https://nextui.org/}{NextUI} to maximize performance and enhance user experience.}

\li{Revamped the online sales journey for SME insurance products, creating a seamless user experience, boosting conversion rates by 22\% and reducing customer drop-off by 35\%.}

\li{Improved page load speeds by 75\% through optimizations, significantly improving the experience across all B2B SME product journeys.}

\ulEnd