%-----------Project 1 ------------
\hTable
{Safeher $|$ Mobile App Development}{\href{https://github.com/Context-Not-Found/Frontend}{Live}}
{Tech Stack: React Native, Expo, Typescript, Web-Sockets, Zustand, Tamagui}{Sept 2023 --- Oct 2023}

\ulStart
\li{Led a team of 5 in developing a mobile application to enhance campus security for female students.}

\li{Integrated an SOS alert system with real-time location sharing, high-risk area mapping, and a community support chat system, reducing emergency response times by 40\%.}

\li{Built incident-specific chat rooms to facilitate communication and assistance during emergencies, leading to a 35\% increase in reported and resolved incidents.}
\ulEnd


%-----------Project 2 ------------
\vspace{-10pt}
\hTable
{Devfolio $|$ Front-End Development}{\href{https://drishxd.dev}{Live}}
{Tech Stack: Next.js, Typescript, GSAP, Contentful CMS, Lenis, Gtag}{Jun 2023 --- Jul 2023}

\ulStart
\li{Created an interactive portfolio website leveraging Next.js, GSAP, and Lenis Scroll to showcase expertise in modern web development and engaging user interfaces.}

\li{Achieved a Google Page-Speed Insights score of 100 and ranked \#1 on Google for the keyword ``Drishxd" by utilizing Static Site Generation (SSG) and Server-Side Rendering (SSR) with Next.js.}

\li{Integrated Contentful as a headless CMS, to efficiently manage content of website across 2 environments ``development" and ``production" to ensure smooth deployment workflow.}
\ulEnd


%-----------Project 3 ------------
\vspace{-10pt}
\hTable
{Zapkart $|$ Full-Stack Development}{\href{https://zapkart.drishxd.dev}{Live}}
{Tech Stack: React.js, Material UI, Commerce.js, React Router, React Hook Form}{Feb 2022 --- Mar 2022}

\ulStart
\li{Developed a feature-rich e-commerce website using React.js and Commerce.js, showcasing expertise in building complex web applications.}

\li{Implemented core functionalities including product browsing, cart management, and secure checkout, supporting over 10 products with multiple variants and colors, enhancing user experience and product selection.}

\li{Streamlined checkout processes by utilizing React Hook Form for advanced form management and integrated a Payment Gateway to enable secure online transactions.}
\ulEnd